---
title: "SQL Data Website"
output: html_document
---
***
## Filtering Columns and Rows

With SQL, One Can Filter Columns With SELECT and Rows With "WHERE." Let's Try An Example With the Lahman Baseball Database. First, We Need to Load the Appropriate Packages. 

```{r warning=FALSE,message=FALSE}
library(Lahman)
library(sqldf)
```


Now, Suppose We Would Like to See the Homerun Totals for the 1927 Yankees. We Could Write the Following:
```{r}
query<-"SELECT playerID,yearID,teamID, HR FROM Batting
WHERE teamID='NYA' and yearID=1927"
sqldf(query)
```
##Examples of More Specific Inquiries 
***
Find All Instances Where Yankees Have Hit 40 Homeruns or More.
```{r}
query<-"SELECT playerID,teamID,yearID,HR FROM Batting
WHERE teamID='NYA' and HR>=40"
sqldf(query)

```
Find All Examples Where a Player Had More Than 40 Homeruns but Less Than 60 Strikeouts.
```{r}
query<-"SELECT playerID,teamID,yearID,HR,SO FROM Batting
WHERE teamID='NYA' and HR>40 and SO<60"
sqldf(query)
```
Find All Instances of Philies in the 1970's Hitting More Than 30 Homeruns.
```{r}
query<-"SELECT playerID,teamID,yearID,HR FROM Batting
WHERE teamID='PHI' and yearID>='1970' and yearID<='1979' and HR>30"
sqldf(query) 
```
Find Every Instance of a Player Hitting More Than 50 Homeruns, but Let's Have the Players With the Most Homeruns on Top.
```{r}
query<-"SELECT playerID,teamID,yearID,HR FROM Batting
WHERE HR>50 
ORDER BY HR DESC"
sqldf(query) 
```
Find All Instances of a Player Striking Out Less Than 10 Times. Make Sure Each Player Had at Least 400 At-Bats. Players With the Least Strikeouts at the Top. 
```{r}
query<-"SELECT playerID,teamID,yearID,SO,AB FROM Batting
WHERE SO<10 and AB>=400
ORDER BY SO"
sqldf(query)
```
##Examples of Aggregation
***
Find the Career Homerun Totals for All Players. Limit the Display to Only Those That Have a Career Total of 600 or More Homeruns. Have the Players With the Highest Total at the Top.
```{r}
query<-"SELECT playerID,sum(HR) FROM Batting 
GROUP BY playerID 
HAVING sum(HR)>=600
ORDER BY sum(HR) DESC"
sqldf(query)
```
Find the Players Who Averaged 30 Homeruns per Season Over Their Career. Put the Players With the Highest Average at the Top.
```{r}
query<-"SELECT playerID,avg(HR) FROM Batting
GROUP BY playerID
HAVING avg (HR)>30
ORDER BY avg(HR) DESC"
sqldf(query)
```
##Joining Master Table 
***
Join Babe Ruth By His First and Last Name.
```{r}
query<-"SELECT nameFirst,nameLast,teamID,yearID,HR
FROM Batting INNER JOIN Master
ON Batting.playerID=Master.playerID
WHERE Batting.playerID='ruthba01'"
sqldf(query)
```
Find All Instances of Players Hitting More Than 50 Homeruns. Give First and Last Names, teamID, yearID and Homeruns. Have the Players With the Highest Homeruns Total at the Top.
```{r}
query<-"SELECT nameFirst,nameLast,teamID,yearID,HR
FROM Batting INNER JOIN Master
ON Batting.playerID=Master.playerID
WHERE HR>50
ORDER BY HR DESC"
sqldf(query)
```
Join Babe Ruth By His Team Name.
```{r}
query<-"SELECT playerID,name,Batting.yearID,Batting.HR
FROM Batting INNER JOIN Teams
ON Batting.teamID=Teams.teamID AND Batting.yearID=Teams.yearID
WHERE playerID='ruthba01'"
sqldf(query)
```
List All Players Named "Bob" Who Averaged More Than One Million Dollars per Year in Sallary for Their Careers. Include Last Names.
```{r}
query<-"SELECT nameFirst,nameLast,avg(salary)
FROM Salaries INNER JOIN Master
ON Salaries.playerID=Master.playerID
WHERE nameFirst='Bob'
GROUP BY Salaries.playerID
HAVING avg(salary)>1000000"

sqldf(query)
```
